---
title: "Conversion of Sweave vignettes to R Markdown"
date: "`r BiocStyle::doc_date()`"
author:
- name: Levi Waldron
  affiliation: CUNY School of Public Health, New York, NY
- name: Marcel Ramos
  affiliation:
    - CUNY School of Public Health, New York, NY
    - Roswell Park Comprehensive Cancer Center, Buffalo, NY
vignette: >
  %\VignetteIndexEntry{Conversion of Sweave vignettes to R Markdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    toc_float: true
package: Rnw2Rmd
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

```{r,include=TRUE,results="hide",message=FALSE,warning=FALSE}
library(Rnw2Rmd)
```

The `Rnw2Rmd` package automates parts of the process of converting Sweave
vignettes to R Markdown (or Quarto). It is employed by the conversion template
for Bioconductor packages at
https://github.com/waldronlab/sweave2rmd_conversiontemplate.

Output Rmd documents will still have to be tested and corrected manually, but
this should be a lot less work than starting from scratch. Please report issues
at https://github.com/Bioconductor/sweave2rmd/issues.

# Usage

We demonstrate usage on demo `Rnw2Rmd-test.Rnw` vignette included in the 
`inst/example` directory of this package:

```{r, message=FALSE}
fpath <- system.file("example/Rnw2Rmd-test.Rnw", package="Rnw2Rmd")
```

Perform the conversion:

```{r}
dir.create(tempdir <- tempfile())
test_rmd <- file.path(tempdir, "Rnw2Rmd-test.Rmd")
Rnw2Rmd(from = fpath, to = test_rmd, validate = TRUE)
```

Note, some validation errors are not actually much of a problem and you can use
`validate=FALSE` to skip validation and still get a useful draft conversion.

# The product

Compare the source document:
```{r,echo=FALSE}
noquote(readLines(fpath))
```

and the generated document:

```{r,echo=FALSE}
noquote(readLines(test_rmd))
```
