---
title: "Conversion of Sweave vignettes to R Markdown"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Conversion of Sweave vignettes to R Markdown}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The Rnw2Rmd package automates parts of the process of converting Sweave vignettes to R Markdown (or Quarto). It is employed by the conversion template for Bioconductor packages at https://github.com/waldronlab/sweave2rmd_conversiontemplate. 

Output Rmd documents will still have to be tested and corrected manually,
but this should be a lot less work than starting from scratch. Please report issues at https://github.com/Bioconductor/sweave2rmd/issues. 

```{r setup}
library(Rnw2Rmd)
```

# Usage

We demonstrate usage on demo `Rnw2Rmd-test.Rnw` vignette included in the 
`inst/example` directory of this package:
```{r, message=FALSE}
fpath <- system.file("example/Rnw2Rmd-test.Rnw", package="Rnw2Rmd")
```

Perform the conversion:
```{r}
Rnw2Rmd(from = fpath, to = "Rnw2Rmd-test.Rmd", validate = TRUE)
```

Note, some validation errors are not actually much of a problem and 
you can use `validate=FALSE` to skip validation and still get a useful draft
conversion. 

# The product

Compare the source document:
```{r}
noquote(readLines(fpath))
```

and the generated document:

```{r}
noquote(readLines("Rnw2Rmd-test.Rmd") )
```

